\documentclass[../recipe-collections/cooking.tex]{subfiles}

\begin{document}
\begin{recipe}{\textbf{Bacon, Potato, Egg Casserole}}{5 large servings}{15 minute prep, 50 minute cook}

  \freeform{}\textit{Bacon Potato, and Egg Casserole – this easy breakfast 
  casserole is packed with bacon, potatoes, and cheese! It can be prepared 
  ahead of time and is a real crowd pleaser!}

  \ing[1]{lb}{bacon, cut in 1/2" strips}

  Heat the oven to 350°F. Grease a 9x13 baking dish with nonstick cooking spray and set aside.
  In a large skillet, cook bacon over medium heat, stirring occasionally. Cook until it is a nice 
  crispy brown. Remove bacon with a slotted spoon and place on a paper towel lined plate. 
  Roughly chop the bacon and set aside.


  \ing[1]{large}{yellow onion, diced}
  \ing[1]{}{bell pepper, diced}
  \ing[3]{cloves}{garlic, minced}

  Add the onion and red pepper to the skillet and cook over medium heat until tender. 
  Add the garlic and cook for 2 minutes. Set aside.

  \ing[12]{large}{eggs}
  \ing[1]{cup}{milk}
  \ing[3]{cups}{potatoes, diced}
  \ing[2]{cups}{cheese, shredded}
  \ing[1 1/2]{tsp}{salt}
  \ing[1/2]{tsp}{black pepper}
  \ing[2]{}{green onions, chopped}

  In a large bowl, beat the eggs and whisk in the milk. Stir in the cooked vegetables, 
  potatoes, and 1 cup of the shredded cheese. Set ¾ cup of bacon aside and stir in the rest. 
  Season with salt and pepper.

  Pour the mixture into the prepared baking dish and top remaining cheese and green onions.
  Bake for 20 minutes so the eggs start to set up. Carefully add the remaining bacon to the 
  top of the casserole. Bake for an additional 20 tot 30 minutes or until the eggs are firm 
  and the top is slightly golden brown. Let stand for 10 minutes. Cut into squares and serve warm.

  \bigskip
  \centering
  \begin{tabular}{|lr|}
    \hline
                                        &                                       \\
    \multicolumn{2}{|l|}{\huge{\textbf{\textrm{Nutrition Facts}}}}              \\
    \multicolumn{2}{|l|}{\textrm{Carrot Cake Baked Oatmeal}}                               \\ 
                                        &                                       \\
    \multicolumn{2}{|l|}{\footnotesize{\textbf{\textrm{Amount per Serving}}}}   \\ \hline
    \textbf{\textrm{Calories (kcal)}}   & \textrm{504}                          \\ \hline
    \textbf{\textrm{Fat (g)}}           & \textrm{28}                           \\ \hline
    \hspace{2mm} \textrm{Sat. Fat (g)}     & \textrm{14}                            \\ \hline
    \textbf{\textrm{Carbohydrates (g)}} & \textrm{30}                            \\ \hline
    \hspace{2mm} \textrm{Sugar (g)}     & \textrm{4}                            \\ \hline
    \hspace{2mm} \textrm{Fiber (g)}     & \textrm{2}                            \\ \hline
    \textbf{\textrm{Protein (g)}} & \textrm{13.28}                            \\ \hline
  \end{tabular}

  \freeform{}\hrulefill{}
  

\end{recipe}

Re-produced from \citetitle{TwoPeasAndTheirPod_BaconPotatoEggCasserole_2020} 
\autocite{TwoPeasAndTheirPod_BaconPotatoEggCasserole_2020}

\end{document}