\documentclass[../recipe-collections/cooking.tex]{subfiles}

\begin{document}
\begin{recipe}{\textbf{Black Pepper Angus Steak}}{3 servings}{}

  \freeform{}\textit{This Panda Express black pepper angus steak 
  recipe consists of deliciously seasoned steak with a sweet and 
  savory sauce that perfectly coats the steak and a blend of 
  veggies. And the best part is this copycat recipe takes only 
  a few simple steps and is ready in under 30 minutes!}

  \ing[12]{ounces}{Angus Sirloin Steak, cut to 1" strips}
  \ing[1]{tablespoons}{cornstarch}
  \ing[1]{tablespoon}{soy sauce}


  In a small bowl, combine the cornstarch and the 1 tablespoon 
  portion of soy sauce. Add the steak slices and coat well. Set 
  aside and marinate in the cornstarch mixture for at least an hour.

  \ing[4]{tablespoons}{soy sauce}
  \ing[2]{tablespoons}{worcestershire sauce}

  In a small bowl add the remaining portion of soy sauce with the 
  kecap manis and Worcestershire sauce. Set aside.

  \ing[2]{tablespoons}{sesame seed oil}
  \ing[1]{teaspoon}{garlic, minced}
  \ing[1]{small}{while onion, cut and sliced into 1" pieces}

  Heat a large skillet or wok over high heat. Add the sesame seed oil 
  and wait for it to start smoking slightly. Add the garlic and onion, 
  and stir fry for 1-2 minutes until the onion begins to get translucent.

  \ing[12]{ounces}{asparagus}
  \ing[1 1/2]{cups}{white mushrooms, sliced}
  \ing[1/2]{cup}{chinese rice wine}
  \ing[1/2]{teaspoon}{black pepper}

  Add the mushrooms and cook for an additional 1-2 minutes. Add the 
  marinated steak and cook until no longer pink (about 4-5 minutes). 
  Add the asparagus, then Chinese Rice Wine, and stir fry for about 
  1 minute before adding the sauce (combined soy sauce, kecap manis, 
  and Worcestershire) and black pepper.

  Cook for 3-4 minutes (covered if you want your Shanghai Angus Steak 
  to be nice and saucy) or until the asparagus has reached your desired 
  level of tenderness and the sauce has thickened. Remove from heat and 
  serve immediately.

  \bigskip
  \centering
  \begin{tabular}{|lr|}
    \hline
                                        &                                       \\
    \multicolumn{2}{|l|}{\huge{\textbf{\textrm{Nutrition Facts}}}}              \\
    \multicolumn{2}{|l|}{\textrm{Black Pepper Angus Steak}}                               \\ 
                                        &                                       \\
    \multicolumn{2}{|l|}{\footnotesize{\textbf{\textrm{Amount per Serving}}}}   \\ \hline
    \textbf{\textrm{Calories (kcal)}}   & \textrm{278}                          \\ \hline
    \textbf{\textrm{Fat (g)}}           & \textrm{16}                           \\ \hline
    \textbf{\textrm{Carbohydrates (g)}} & \textrm{7}                            \\ \hline
    \textbf{\textrm{Protein (g)}}       & \textrm{25}                            \\ \hline
  \end{tabular}

  \freeform{}\hrulefill{}

\end{recipe}

Re-produced from \citetitle{ImHungryForThat_BlackPepperAngusSteak_2022} 
\autocite{ImHungryForThat_BlackPepperAngusSteak_2022}
\end{document}