\documentclass[../recipe-collections/cooking.tex]{subfiles}

\begin{document}
\begin{recipe}{\textbf{Instant Pot Black-Eyed Peas and Collard Greens}}{6 servings}{}

  \freeform{}\textit{Instant Pot Black-Eyed Peas and Collard Greens}

  \freeform{}\textit{Collard Greens}

  
  \ing[\fr12]{pound}{Pork Belly, Diced}

  On the Instant Pot, hit “Sauté” and “Adjust” so it’s on the “Normal” or 
  “Medium” setting. When the pot display reads “Hot,” add the pork belly and 
  stir for 1 minute. Don’t let it cook too long. Just enough for the pork 
  belly to sweat and release some grease

  \ing[1 \fr14]{pound}{Collard Greens}
  \ing[\fr12]{large}{White Onion, Diced}
  \ing[6]{cloves}{Garlic, Diced}
  \ing[4]{cups}{Ham Broth}

  Add in the broth, onion, garlic and finish with the collard greens. Press 
  the greens down good so they’re fully in the pot and don’t worry if they are 
  too close to the lid – they cook down significantly. Do not stir them up 
  with the broth

  Secure the lid, hit “Keep Warm/Cancel” and select “Manual” or “Pressure 
  Cook” High Pressure for 60 minutes. Perform a quick release when done (Note: 
  they may smell a little pungent when quick releasing. That means you’ve 
  made ’em right!)

  Add in the kosher salt and stir. Let cool for 10 minutes, plate and 
  top with pepper sauce if desired

  \freeform{}\textit{Black-Eyed Peas}

  \ing[1]{pound}{Dried Black-Eyed Peas}
  \ing[3]{cups}{Chicken Broth}
  \ing[3]{cups}{Ham Broth}
  \ing[\fr12]{large}{White Onion, Diced}
  \ing[\fr12]{pound}{Pork Belly, Diced}

  Add the broth, pork belly, onion and black-eyed peas to the Instant Pot. 
  Stir well.

  Add in a clean penny for good luck

  Secure the lid and select “Manual” or “Pressure Cook” High Pressure for 30 
  minutes. Allow a 30 minute natural release when done and follow with a 
  quick release

  Stir everything, let cool for 10 minutes (it will thicken up when really 
  cooled down), plate and top with some Chow Chow and a little mayonnaise if 
  desired and mix together well

  Enjoy and whoever gets the penny in their bowl should prosper extra well 
  this year!

\end{recipe}

Re-produced from \citetitle{PressureLuck_BlackEyedPeasAndGreens_2017} \autocite{PressureLuck_BlackEyedPeasAndGreens_2017}

\end{document}