\documentclass[../recipe-collections/cooking.tex]{subfiles}

\begin{document}
\begin{recipe}{\textbf{Breakfast Burritos}}{8 serving}{}

  \freeform{}\textit{These burritos can be made for meal-prep. Store in the refridgerator,
  microwave them at 70\% power for 2 minutes, flip the burrito and microwave at full power
  for another 20 seconds.}

  \ing[1]{}{\href{https://www.dillons.com/p/russet-potato/0000000004072}
  {russet potato}}
  \ing[3]{tbsp}{\href{https://www.dillons.com/p/simple-truth-organic-refined-avocado-oil-bottle/0001111003441}
  {avocado oil}}
  \ing[]{}{salt}
  \ing[]{}{pepper}

  Preheat the oven to 400F. Line a sheet pan with parchment paper. 
  Shred the potato. In a mixing bowl, mix the potato, avocado oil, salt, and
  pepper. Distribute the mixture onto the pan lined with parchment paper. Place 
  the pan in the preheated oven and bake for 30 minutes or until crispy brown.

  \ing[1]{dozen}{\href{https://www.dillons.com/p/simple-truth-natural-cage-free-large-brown-eggs/0001111079770}
  {eggs}}
  \ing[2]{4 oz can}{\href{https://www.dillons.com/p/kroger-diced-green-chile-peppers/0001111084009}
  {diced green chiles}}
  \ing[]{}{salt}
  \ing[]{}{pepper}

  Crack the eggs into a mixing bowl, add the green chiles, salt, and pepper. Mix 
  the egg mixture.

  \ing[1]{12 oz package}{\href{https://www.dillons.com/p/kroger-original-breakfast-sausage-links/0001111097293}
  {breakfast sausage links}}

  Dice the sausage links and brown them in a skillet. Add the egg mixture and cook
  it. 
  
  \ing[8]{}{\href{https://www.dillons.com/p/mission-carb-balance-low-carb-whole-wheat-burrito-tortillas/0007373100118}
  {low carb tortillas}}
  \ing[2]{cups}{\href{https://www.dillons.com/p/kroger-shredded-mexican-style-cheese-blend/0001111050204}
  {shredded mexican cheese blend}}

  Spread 1/8th of the potatoes on a tortilla. Layer in some cheese. Add 1/8th of 
  the eggs on top of the cheese and potatoes, then layer on some more cheese. 
  Roll up the tortilla and wrap it in aluminum foil if saving for later. Repeat
  the process for the remaining 7 burritos.

  \bigskip
  \centering
  \begin{tabular}{|lr|}
      \hline
      & \\
      \multicolumn{2}{|l|}{\huge{\textbf{\textrm{Nutrition Facts}}}}
      \\ [0.5ex] \hline
      \multicolumn{2}{|l|}{\textrm{Serving Size: 1}} \\ [0.5ex]
      \multicolumn{2}{|l|}{\textrm{Servings per Recipe:  8 }}
      \\ \noalign{\hrule height 3pt}
      \multicolumn{2}{|l|}{\footnotesize{\textbf{\textrm{Amount per Serving}}}}
      \\
      \textbf{\textrm{Calories (kcal)}}            & \textbf{ 491.62 }
      \\ \noalign{\hrule height 2pt}
      \textbf{\textrm{Fat (g)}}                      & \textrm{ 33.1 }  \\ \hline
      \hspace{2mm} \textrm{Saturated Fat (g)}        & \textrm{ 11.86 }  \\ \hline
      \hspace{2mm} \textrm{Trans Fat (g)}            & \textrm{ 0.0 }      \\ \hline
      \hspace{2mm} \textrm{Polyunsaturated Fat (g)}  & \textrm{ 2.26 }   \\ \hline
      \hspace{2mm} \textrm{Monounsaturated Fat (g)}  & \textrm{ 6.75 }   \\ \hline
      \textbf{\textrm{Cholesterol (mg)}}             & \textrm{ 327.81 }  \\ \hline
      \textbf{\textrm{Sodium (mg)}}                  & \textrm{ 1428.69 } \\ \hline
      \textbf{\textrm{Carbohydrates (g)}}            & \textrm{ 38.94 }  \\ \hline
      \hspace{2mm} \textrm{Sugar (g)}                & \textrm{ 0.8 }   \\ \hline
      \hspace{2mm} \textrm{Fiber (g)}                & \textrm{ 23.57 }  \\ \hline
      \textbf{\textrm{Protein (g)}}                  & \textrm{ 29.21 }
      \\ \noalign{\hrule height 3pt}
      \textbf{Calcium} \textrm{ 341.43  mg}      &
      \multicolumn{1}{|l|}{\textbf{Iron} \textrm{ 3.08  mg}}            \\ \hline
      \textbf{Phosphorus} \textrm{ 150.0  mg}   &
      \multicolumn{1}{|l|}{\textbf{Potassium} \textrm{ 297.31  mg}}     \\ \hline
      \textbf{Riboflavin} \textrm{ 0.39  mg}  &
      \multicolumn{1}{|l|}{\textbf{Vitamin A} \textrm{ 450.0 IU }}        \\ \hline
      \textbf{Vitamin C} \textrm{ 0.0  mg}      &
      \multicolumn{1}{|l|}{\textbf{Vitamin D} \textrm{ 60.0  IU}}         \\ \hline
      \textbf{Vitamin E} \textrm{ 12.0  IU}     &
      \multicolumn{1}{|l|}{\textbf{Zinc} \textrm{ 0.0  mg}}               \\ \hline
  \end{tabular}

  \freeform{}\hrulefill{}

\end{recipe}

Adapted from \citetitle{Pillsbury_BreakfastBurritos_2021} 
\autocite{Pillsbury_BreakfastBurritos_2021} and
\citetitle{MirlandrasKitchen_HashBrowns_2017}
\autocite{MirlandrasKitchen_HashBrowns_2017}

\end{document}