\documentclass[../recipe-collections/cooking.tex]{subfiles}

\begin{document}
\begin{recipe}{\textbf{Carrot Cake Baked Oatmeal}}{6 servings}{1 hour 15 minutes}

  \freeform{}\textit{This Carrot Cake Baked Oatmeal is packed with 
  good-for-you carrots, only a little sugar, and pops of sweetness 
  from raisins and a cheesecake-inspired topping. }

  \ing[1]{pound}{carrots}

  Preheat the oven to 375ºF. Peel or scrub the carrots, then slice them 
  into rounds. Boil or steam the carrots until they are extremely soft 
  (I steamed for 15 minutes, but this will depend on the size of your carrots).

  \ing[2]{large}{eggs}
  \ing[1/3]{cup}{brown sugar}
  \ing[1/2]{tsp}{cinnamon}
  \ing[1/4]{tsp}{ground nutmeg}
  \ing[1]{tsp}{baking powder}
  \ing[1/2]{tsp}{salt}

  Place the cooked carrots in a large bowl and mash with a potato masher. 
  Add the eggs, brown sugar, cinnamon, nutmeg, baking powder, and salt. 
  Whisk these ingredients together until well combined.

  \ing[2]{cups}{milk}
  \ing[3]{cups}{old-fashioned rolled oats}
  \ing[1/3]{cup}{chopped walnuts}
  \ing[1/3]{cup}{raisins}

  Add the milk to the bowl and whisk until combined again. Finally, add the 
  rolled oats, walnuts, and raisins and stir with a large spoon until combined. 
  Pour the oat mixture into a 3 quart casserole dish coated with non-stick spray.

  \ing[4]{ounces}{cream cheese, room temperature}
  \ing[1]{large}{egg yolk}
  \ing[1/4]{tsp}{vanilla extract}
  \ing[1]{tsp}{lemon juice}
  \ing[2]{tbsps}{sugar}

  In a separate small bowl, combine the cream cheese, egg yolk, vanilla, 
  lemon juice, and sugar. Whisk or stir with a fork until smooth. If needed, 
  microwave for 15 seconds to slightly warm the cream cheese mixture so it 
  is slightly more fluid, then drizzle it over the oat mixture in the 
  casserole dish.

  Bake the Carrot Cake Oatmeal for 45 minutes, or until the cream cheese 
  mixture is slightly golden brown on top. Serve immediately, or divide 
  into single portions, then refrigerate.

  \bigskip
  \centering
  \begin{tabular}{|lr|}
    \hline
                                        &                                       \\
    \multicolumn{2}{|l|}{\huge{\textbf{\textrm{Nutrition Facts}}}}              \\
    \multicolumn{2}{|l|}{\textrm{Carrot Cake Baked Oatmeal}}                               \\ 
                                        &                                       \\
    \multicolumn{2}{|l|}{\footnotesize{\textbf{\textrm{Amount per Serving}}}}   \\ \hline
    \textbf{\textrm{Calories (kcal)}}   & \textrm{438.3}                          \\ \hline
    \textbf{\textrm{Fat (g)}}           & \textrm{14.82}                           \\ \hline
    \textbf{\textrm{Carbohydrates (g)}} & \textrm{59.2}                            \\ \hline
    \hspace{2mm} \textrm{Fiber (g)}     & \textrm{6.88}                            \\ \hline
    \textbf{\textrm{Protein (g)}} & \textrm{13.28}                            \\ \hline
  \end{tabular}

  \freeform{}\hrulefill{}
  

\end{recipe}

Re-produced from \citetitle{BudgetBytes_CarrotCake_2019} 
\autocite{BudgetBytes_CarrotCake_2019}

\end{document}