\documentclass[../recipe-collections/cooking.tex]{subfiles}

\begin{document}
\begin{recipe}{\textbf{Lower Carb Carrot Cake Baked Oatmeal}}{6 servings}{1 hour 15 minutes}

  \freeform{}\textit{This Carrot Cake Baked Oatmeal is adapted from the original
  recipe to be lower in carbohydrates.}

  \ing[1]{pound}{carrots}

  Preheat the oven to 375ºF. Peel or scrub the carrots, then slice them 
  into rounds. Boil or steam the carrots until they are extremely soft 
  (I steamed for 15 minutes, but this will depend on the size of your carrots).

  \ing[2]{large}{eggs}
  \ing[1/3]{cup}{\href{https://www.dillons.com/p/swerve-brown-sugar-replacement/0085270030037}{Swerve Brown Sugar Replacement}}
  \ing[1/2]{tsp}{cinnamon}
  \ing[1/4]{tsp}{ground nutmeg}
  \ing[1]{tsp}{baking powder}
  \ing[1/2]{tsp}{salt}

  Place the cooked carrots in a large bowl and mash with a potato masher. 
  Add the eggs, \href{https://www.dillons.com/p/swerve-brown-sugar-replacement/0085270030037}{Swerve Brown Sugar Replacement}, 
  cinnamon, nutmeg, baking powder, and salt. 
  Whisk these ingredients together until well combined.

  \ing[2]{cups}{\href{https://www.dillons.com/p/kroger-carbmaster-ultra-filtered-skim-milk/0001111008303}{CARBmaster Ultra-Filtered Skim Milk}}
  \ing[3]{cups}{old-fashioned rolled oats}
  \ing[1/3]{cup}{chopped walnuts}
  \ing[1/3]{cup}{raisins}

  Add the milk to the bowl and whisk until combined again. Finally, add the 
  rolled oats, walnuts, and raisins and stir with a large spoon until combined. 
  Pour the oat mixture into a 3 quart casserole dish coated with non-stick spray.

  \ing[4]{ounces}{cream cheese, room temperature}
  \ing[1]{large}{egg yolk}
  \ing[1/4]{tsp}{vanilla extract}
  \ing[1]{tsp}{lemon juice}
  \ing[2]{tbsps}{\href{https://www.dillons.com/p/swerve-granular-zero-calorie-sweetener/0085270030017}{Swerve Granular Zero Calorie Sweetener}}

  In a separate small bowl, combine the cream cheese, egg yolk, vanilla, 
  lemon juice, and \href{https://www.dillons.com/p/swerve-granular-zero-calorie-sweetener/0085270030017}{Swerve Granular Zero Calorie Sweetener}. 
  Whisk or stir with a fork until smooth. If needed, 
  microwave for 15 seconds to slightly warm the cream cheese mixture so it 
  is slightly more fluid, then drizzle it over the oat mixture in the 
  casserole dish.

  Bake the Carrot Cake Oatmeal for 45 minutes, or until the cream cheese 
  mixture is slightly golden brown on top. Serve immediately, or divide 
  into single portions, then refrigerate.

  \bigskip
  \centering
  \begin{tabular}{|lr|}
    \hline
    & \\
    \multicolumn{2}{|l|}{\huge{\textbf{\textrm{Nutrition Facts}}}}
    \\ [0.5ex] \hline
    \multicolumn{2}{|l|}{\textrm{Serving Size: 1}} \\ [0.5ex]
    \multicolumn{2}{|l|}{\textrm{Servings per Recipe:  6 }}
    \\ \noalign{\hrule height 3pt}
    \multicolumn{2}{|l|}{\footnotesize{\textbf{\textrm{Amount per Serving}}}}
    \\
    \textbf{\textrm{Calories (kcal)}}            & \textbf{ 308.78 }
    \\ \noalign{\hrule height 2pt}
    \textbf{\textrm{Fat (g)}}                      & \textrm{ 12.96 }  \\ \hline
    \hspace{2mm} \textrm{Saturated Fat (g)}        & \textrm{ 3.67 }  \\ \hline
    \hspace{2mm} \textrm{Trans Fat (g)}            & \textrm{ 0.0 }      \\ \hline
    \hspace{2mm} \textrm{Polyunsaturated Fat (g)}  & \textrm{ 0.0 }   \\ \hline
    \hspace{2mm} \textrm{Monounsaturated Fat (g)}  & \textrm{ 0.0 }   \\ \hline
    \textbf{\textrm{Cholesterol (mg)}}             & \textrm{ 106.0 }  \\ \hline
    \textbf{\textrm{Sodium (mg)}}                  & \textrm{ 370.35 } \\ \hline
    \textbf{\textrm{Carbohydrates (g)}}            & \textrm{ 55.9 }  \\ \hline
    \hspace{2mm} \textrm{Sugar Alcohols (g)}       & \textrm{ 18.67 }   \\ \hline
    \hspace{2mm} \textrm{Sugar (g)}                & \textrm{ 8.71 }   \\ \hline
    \hspace{2mm} \textrm{Fiber (g)}                & \textrm{ 4.98 }  \\ \hline
    \textbf{\textrm{Protein (g)}}                  & \textrm{ 13.14 }
    \\ \noalign{\hrule height 3pt}
    \textbf{Calcium} \textrm{ 186.92  mg}      &
    \multicolumn{1}{|l|}{\textbf{Iron} \textrm{ 2.17  mg}}            \\ \hline
    \textbf{Phosphorus} \textrm{ 0.0  mg}   &
    \multicolumn{1}{|l|}{\textbf{Potassium} \textrm{ 238.48  mg}}     \\ \hline
    \textbf{Riboflavin} \textrm{ 0.0  mg}  &
    \multicolumn{1}{|l|}{\textbf{Vitamin A} \textrm{ 72.72 IU }}        \\ \hline
    \textbf{Vitamin C} \textrm{ 0.0  mg}      &
    \multicolumn{1}{|l|}{\textbf{Vitamin D} \textrm{ 52.67  IU}}         \\ \hline
    \textbf{Vitamin E} \textrm{ 0.0  IU}     &
    \multicolumn{1}{|l|}{\textbf{Zinc} \textrm{ 0.0  mg}}               \\ \hline
\end{tabular}

  \freeform{}\hrulefill{}
  

\end{recipe}

Re-produced from \citetitle{BudgetBytes_CarrotCake_2019} 
\autocite{BudgetBytes_CarrotCake_2019}

\end{document}