\documentclass[../recipe-collections/cooking.tex]{subfiles}

\begin{document}
\begin{recipe}{\textbf{Pulled Pork Burritos}}{8 serving}{}

  \freeform{}\textit{These burritos can be made for meal-prep. Store in the refridgerator,
  microwave them at 60\% power for 2 minutes, flip the burrito and microwave at full power
  for another 15 seconds.}

  \ing[\fr34]{lb}{pulled pork}

  Prepare the pulled pork, place in a mixing bowl.

  \ing[3]{tbsp}{\href{https://www.dillons.com/p/simple-truth-organic-refined-avocado-oil-bottle/0001111003441}
  {avocado oil}}
  \ing[1]{large}{\href{https://www.dillons.com/p/large-green-bell-pepper/0000000004065}
  {green bell pepper, diced}}
  \ing[\fr12]{jumbo}{\href{https://www.dillons.com/p/jumbo-red-onions/0000000004082}
  {red onion, diced}}
  \ing[2]{cloves}{\href{https://www.dillons.com/p/garlic/0000000004608}
  {garlic}}

  In a saucepan, fry the bell peppers, onion, and garlic in oil until the onions 
  are translucent. Place in the mixing bowl.

  \ing[12]{ounce}{\href{https://www.dillons.com/p/kroger-recipe-beginnings-frozen-riced-cauliflower/0001111080650}
  {frozen cauliflower rice}}
  
  Preheat the oven to 425F. Defrost the cauliflower rice in a microwave as instructed
  on the bag. Spread the cauliflower rice on sheet pan lined with parchment paper. 
  Bake the cauliflower rice for 12 minutes. Add the cauliflower rice to the mixing 
  bowl.

  \ing[3]{tbsp}{\href{https://www.dillons.com/p/cilantro/0000000004889}
  {cilantro, chopped}}
  \ing[1]{can}{\href{https://www.dillons.com/p/kroger-black-beans/0001111072567}
  {black beans, drained}}
  \ing[2]{tsp}{\href{https://www.dillons.com/p/kroger-salt/0001111004807}
  {salt}}
  \ing[1]{tsp}{\href{https://www.dillons.com/p/kroger-coarse-ground-black-pepper/0001111000719}
  {ground black pepper}}

  Add the cilantro, black beans, salt, and pepper to the mixing bowl.

  \ing[\fr12]{large}{\href{https://www.dillons.com/p/large-limes/0000000004048}
  {lime}}

  Zest and juice the lime, add it to the mixing bowl.

  \ing[8]{}{\href{https://www.dillons.com/p/mission-carb-balance-low-carb-whole-wheat-burrito-tortillas/0007373100118}
  {low carb tortillas}}
  \ing[2]{cups}{\href{https://www.dillons.com/p/kroger-shredded-mexican-style-cheese-blend/0001111050204}
  {shredded mexican cheese blend}}

  Layer some cheese of a tortilla. Add 1/8th of the mixture on top of the cheese, 
  then layer on some more cheese. Roll up the tortilla and wrap it in aluminum 
  foil if saving for later. Repeat the process for the remaining 7 burritos.

  \vspace{0.25in}

  \centering
  \begin{table}[H]
  \begin{tabular}{|lr|}
      \hline
      & \\
      \multicolumn{2}{|l|}{\huge{\textbf{\textrm{Nutrition Facts}}}}
      \\ [0.5ex] \hline
      \multicolumn{2}{|l|}{\textrm{Serving Size: 1}} \\ [0.5ex]
      \multicolumn{2}{|l|}{\textrm{Servings per Recipe:  8 }}
      \\ \noalign{\hrule height 3pt}
      \multicolumn{2}{|l|}{\footnotesize{\textbf{\textrm{Amount per Serving}}}}
      \\
      \textbf{\textrm{Calories (kcal)}}            & \textbf{ 382.92 }
      \\ \noalign{\hrule height 2pt}
      \textbf{\textrm{Fat (g)}}                      & \textrm{ 22.59 }  \\ \hline
      \hspace{2mm} \textrm{Saturated Fat (g)}        & \textrm{ 8.11 }  \\ \hline
      \hspace{2mm} \textrm{Trans Fat (g)}            & \textrm{ 0.0 }      \\ \hline
      \hspace{2mm} \textrm{Polyunsaturated Fat (g)}  & \textrm{ 0.75 }   \\ \hline
      \hspace{2mm} \textrm{Monounsaturated Fat (g)}  & \textrm{ 3.75 }   \\ \hline
      \textbf{\textrm{Cholesterol (mg)}}             & \textrm{ 54.06 }  \\ \hline
      \textbf{\textrm{Sodium (mg)}}                  & \textrm{ 1487.53 } \\ \hline
      \textbf{\textrm{Carbohydrates (g)}}            & \textrm{ 30.77 }  \\ \hline
      \hspace{2mm} \textrm{Sugar (g)}                & \textrm{ 1.7 }   \\ \hline
      \hspace{2mm} \textrm{Fiber (g)}                & \textrm{ 20.75 }  \\ \hline
      \textbf{\textrm{Protein (g)}}                  & \textrm{ 25.79 }
      \\ \noalign{\hrule height 3pt}
      \textbf{Calcium} \textrm{ 355.73  mg}      &
      \multicolumn{1}{|l|}{\textbf{Iron} \textrm{ 1.52  mg}}            \\ \hline
      \textbf{Phosphorus} \textrm{ 0.0  mg}   &
      \multicolumn{1}{|l|}{\textbf{Potassium} \textrm{ 485.67  mg}}     \\ \hline
      \textbf{Riboflavin} \textrm{ 0.0  mg}  &
      \multicolumn{1}{|l|}{\textbf{Vitamin A} \textrm{ 0.0 IU }}        \\ \hline
      \textbf{Vitamin C} \textrm{ 17.09  mg}      &
      \multicolumn{1}{|l|}{\textbf{Vitamin D} \textrm{ 0.0  IU}}         \\ \hline
      \textbf{Vitamin E} \textrm{ 0.0  IU}     &
      \multicolumn{1}{|l|}{\textbf{Zinc} \textrm{ 0.0  mg}}               \\ \hline
  \end{tabular}
  \end{table}


  \freeform{}\hrulefill{}

\end{recipe}

\end{document}