\documentclass[../recipe-collections/cooking.tex]{subfiles}

\begin{document}
\begin{recipe}{\textbf{Super Greens}}{8 servings}{}

  \freeform{}\textit{Panda Express Super Greens Copycat Recipe: 
  A light and zesty blend of broccoli, kale, and cabbage kissed 
  with sauce, just like Panda Express makes it!}

  \ing[2]{tablespoons}{butter}
  \ing[2]{cloves}{garlic, minced}
  \ing[1/2]{teaspoons}{ground ginger}
  \ing[1/2]{teaspoons}{crushed red pepper}

  Place a large saute pan (with a lid) over medium-high heat. 
  Add the butter, garlic, ground ginger, and crushed red pepper. 

  \ing[2]{tablespoons}{soy sauce}
  \ing[6]{tablespoons}{water}

  Once the butter melts saute the garlic for 1 minute, then add 
  in the soy sauce and water.

  \ing[6]{cups}{roughly chopped kale, lightly packed}
  \ing[4]{cups}{broccoli florets}
  \ing[4]{cups}{roughly chopped green cabbage}

  Add the broccoli first, then the cabbage and the kale on top. 
  Cover the saute pan and steam the vegetables for 3-4 minutes. 
  The broccoli should still be firm, not soft in the middle. 

  Toss the vegetables to coat in sauce. Serve warm. 

  \bigskip
  \centering
  \begin{tabular}{|lr|}
    \hline
                                        &                                       \\
    \multicolumn{2}{|l|}{\huge{\textbf{\textrm{Nutrition Facts}}}}              \\
    \multicolumn{2}{|l|}{\textrm{Super Greens}}                               \\ 
                                        &                                       \\
    \multicolumn{2}{|l|}{\footnotesize{\textbf{\textrm{Amount per Serving}}}}   \\ \hline
    \textbf{\textrm{Calories (kcal)}}   & \textrm{77}                          \\ \hline
    \textbf{\textrm{Fat (g)}}           & \textrm{3}                           \\ \hline
    \textbf{\textrm{Carbohydrates (g)}} & \textrm{7}                            \\ \hline
    \hspace{2mm} \textrm{Fiber (g)}     & \textrm{2}                            \\ \hline
    \textbf{\textrm{Protein (g)}}       & \textrm{4}                            \\ \hline
  \end{tabular}

  \freeform{}\hrulefill{}

\end{recipe}

Re-produced from \citetitle{ASpicyPerspective_PandaExpressSuperGreens_2019} 
\autocite{ASpicyPerspective_PandaExpressSuperGreens_2019}
\end{document}